Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials

### 2022-09-23 study protocol.qmd
Update study protocol.qmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tableone)
library(data.table)
library(haven) # Importing SAS Files

@@

## Table 1 ATACH-2

```{r ATACH table1, echo=FALSE}

atach.table1.data <- atach.whole %>%
  select(atachVarsTableOne)

CreateTableOne(vars = atachVarsTableOne,
               data = atach.whole,
               strata = "ich.laterality")

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)

@@

@@

atach.erich %>%
  as_tibble()
